Tropical Mathematics for the Lambda Calculus

### 2023-01-19 appIII.tex
commit

\subsubsection{The language $\BSTLC$}
In Section 4 we considered a variant $\BSTLC$ of $\STLC$ with affine simple types and an exponential $!_{r}A$, for all $r\in \BB R_{\geq 0}$, corresponding to a fragment of $\mathrm{Fuzz}$ \cite{Reed_2010}. 
We describe the rules of this fragment in Fig.~\ref{fig:fuzz}.
The terms are generated by the grammar:

{
\begin{minipage}{\textwidth}
\begin{align*}
t,u:= x\mid \lambda x.t\mid tu \mid !t \mid \mathsf{let} !x=t\mathsf{in} u\mid (t,u)\mid  \mathsf{let} (x,y)=t\mathsf{in} u 
\end{align*}\end{minipage}}\medskip\\
For the purposes of this article we limited ourselves to a minimal fragment of this language. For a more practical language see \cite{Reed_2010,Gaboardi2017}.  
Simple types are generated by the grammar below:

{
\begin{minipage}{\textwidth}
\begin{align*}
A,B:= X\mid !_{r}A \quad (r\in \BB R_{\geq 0}) \mid A\multimap B \mid A\otimes B
\end{align*}\end{minipage}}\medskip\\
Type judgements are of the form $\Gamma \vdash t:A$, where a context $\Gamma$ is a list of declarations of the form $x\in_{r}A$, for some $r\in \BB R_{\geq 0}$.
We define the following operation $\Gamma+\Delta$  as follows:

{
\begin{minipage}{\textwidth}
\begin{align*}
() + () & =() \\
(\Gamma, x\in_{r} A)+( \Delta, x\in_{s} A) & =  (\Gamma+\Delta), x\in_{r+s}A \\
(\Gamma, x\in_{r}A)+\Delta & =(\Gamma+\Delta), x\in_{r}A \qquad (x\notin \Delta) \\
\Gamma+ (\Delta, x\in_{r}A) &= (\Gamma+\Delta), x\in_{r} A \qquad (x\notin \Gamma)
\end{align*}\end{minipage}}\medskip\\
Moreover, we let $s\Gamma$ be the context made all judgmenets $x\in_{sr}A$, where $(x\in_{r}A)\in \Gamma$.

@@

  {
\AXC{$x\in_{r} A\in \Gamma$}
\UIC{$\Gamma\vdash x\in A$}
\DP}

@@

  {
\AXC{$\Gamma\vdash t\in A \otimes B$}
\AXC{$\Delta,x\in_{r}A, y\in_{r} B\vdash u:C$}
\BIC{$\Gamma+\Delta \vdash \mathsf{let} (x,y)=t \mathsf{in} u\in C$}
\DP}
\\
&

@@

  {
\AXC{$\Gamma \vdash t\in A$}
\UIC{$s\Gamma \vdash !t \in \ !_{s}A$}
\DP}

@@

  {
\AXC{$\Gamma\vdash t\in !_{s}A$}
\AXC{$\Delta,x\in_{rs}A\vdash u:C$}
\BIC{$r\Gamma+\Delta \vdash \mathsf{let} !x=t \mathsf{in} u\in C$}
\DP}

@@

\begin{definition}
We define the following structure $(M,w,c,\epsilon,\delta)$ over the category $\LREL$ as follows:
\begin{itemize}
\item for any set $X$ and $n\in \BB N$, let $M(n)(X)=\C M_{\leq n}(X)$;

\item for all $f: X\times Y\to \Lawv$, let $M(n)(f): M(n)(X)\times M(n)(Y)\to \Lawv$ be defined by 
\begin{align*}
M(n)(f)(\alpha,\beta)=
\begin{cases}
\min_{\sigma\in \F S_{k}}\sum_{i=1}^{k}f(x_{i},y_{\sigma(i)}) & 
\text{ if }\alpha=[x_{1},\dots, x_{k}], \beta=[y_{1},\dots, y_{k}]\\
\infty & \text{ otherwise}
\end{cases}
\end{align*}

@@

Let us check that this defines a $\BB N$-graded linear exponential comonad.

\begin{itemize}

@@

>>>>

\subsubsection{The language $\BSTLC$}
In Section 4 we considered a variant $\BSTLC$ of $\STLC$ with affine simple types and an exponential $!_{n}A$, for all $n\in \BB N$, corresponding to a fragment of $\mathrm{Fuzz}$ \cite{Reed2010}. 
We describe the rules of this fragment in Fig.~\ref{fig:fuzz}.
The terms are generated by the grammar:

{
\begin{minipage}{\textwidth}
\begin{align*}
t,u:= x\mid \lambda x.t\mid tu \mid !t \mid \mathsf{let}\  !x=t \ \mathsf{in}\  u\mid (t,u)\mid  \mathsf{let}\  (x,y)=t \ \mathsf{in} \  u 
\end{align*}\end{minipage}}\medskip\\
For the purposes of this article we limited ourselves to a minimal fragment of this language. For a more practical language see \cite{Reed2010,Gaboardi2017}.  
Simple types are generated by the grammar below:

{
\begin{minipage}{\textwidth}
\begin{align*}
A,B:= X\mid  !_{n}A  \mid A\multimap B \mid A\otimes B
\end{align*}\end{minipage}}\medskip\\
Type judgements are of the form $\Gamma \vdash t:A$, where a context $\Gamma$ is a list of declarations of the form $x\in_{n}A$.
We define the following operation $\Gamma+\Delta$  as follows:

{
\begin{minipage}{\textwidth}
\begin{align*}
() + () & =() \\
(\Gamma, x\in_{m} A)+( \Delta, x\in_{n} A) & =  (\Gamma+\Delta), x\in_{m+n}A \\
(\Gamma, x\in_{m}A)+\Delta & =(\Gamma+\Delta), x\in_{n}A \qquad (x\notin \Delta) \\
\Gamma+ (\Delta, x\in_{m}A) &= (\Gamma+\Delta), x\in_{n} A \qquad (x\notin \Gamma)
\end{align*}\end{minipage}}\medskip\\
Moreover, we let $m\Gamma$ be the context made all judgmenets $x\in_{mn}A$, where $(x\in_{n}A)\in \Gamma$.

@@

  {
\AXC{$x\in_{n} A\in \Gamma$}
\UIC{$\Gamma\vdash x\in A$}
\DP}

@@

  {
\AXC{$\Gamma\vdash t\in A \otimes B$}
\AXC{$\Delta,x\in_{n}A, y\in_{n} B\vdash u:C$}
\BIC{$n\Gamma+\Delta \vdash \mathsf{let}\  (x,y)=t \ \mathsf{in}  \ u\in C$}
\DP}
\\
&

@@

  {
\AXC{$\Gamma \vdash t\in A$}
\UIC{$s\Gamma \vdash !t \in \ !_{n}A$}
\DP}

@@

  {
\AXC{$\Gamma\vdash t\in !_{n}A$}
\AXC{$\Delta,x\in_{mn}A\vdash u:C$}
\BIC{$m\Gamma+\Delta \vdash \mathsf{let}\  !x=t \ \mathsf{in} \ u\in C$}
\DP}

@@

\begin{definition}
We define the following structure $(!_{-}(-),w,c,\epsilon,\delta)$ over the category $\LREL$ as follows:
\begin{itemize}
\item for any set $X$ and $n\in \BB N$, let $!_{n}(X)=\C M_{\leq n}(X)$;

\item for all $f: X\times Y\to \Lawv$, let $!_{n}(f): !_{n}(X)\times !_{n}(Y)\to \Lawv$ be defined by 
\begin{align*}
!_{n}(f)(\alpha,\beta)=
\begin{cases}
\min_{\sigma\in \F S_{k}}\sum_{i=1}^{k}f(x_{i},y_{\sigma(i)}) & 
\text{ if }\alpha=[x_{1},\dots, x_{k}], \beta=[y_{1},\dots, y_{k}]\\
\infty & \text{ otherwise}
\end{cases}
\end{align*}

@@

\begin{proposition}
 $(!_{-}(-),w,c,\epsilon,\delta)$  is a $\BB N$-graded linear exponential comonad over $\LREL$.
\end{proposition}
\begin{proof}
\begin{itemize}

@@

\end{itemize}
\end{proof}
